
%Generally, the cover letter should include the following:
% - Introduction
% - Description of work done since last delivery (i.e. progress report).
% - List of items in current delivery.
% - Standard business letter format
%   (https://owl.english.purdue.edu/owl/resource/653/01/

\documentclass[12pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage[pdftex]{hyperref}
\usepackage[english]{babel}

\setlength\parindent{0pt}
\setlength\parskip{1em}

\newcommand\tab[1][.5in]{\hspace*{#1}}

\begin{document}

\hfill Feb 24, 2017

\hfill Epsilon Games

Mark Baldwin,

We have made significant progress on \textit{{\AE}on Chronicles} since we last
spoke. We intend to continue at this quick pace in order to keep up with the
rapid milestone schedule we have set for ourselves.

Since the last delivery, we have completed a number of major items. At the most
basic level, we have completed overworld movement mechanics for our main
character. We have a framework for NPC interaction set up. Furthermore, hooks
to begin combat have been added. Lastly, we added a very basic start menu, which
can be extended easily.

This delivery consists of one main item, our new game code. This code only has
a few rooms for now, but any more than that was not planned to be a part of 
this delivery. All of these features are present in the room called rm\_forest 
which can be accessed from the title screen.

In this room there is a player controlled character denoted currently by a 
black circle with an "x" in it, an NPC denoted by a red square with a smiley 
face, and two enemies. The NPC and enemies can be interacted with.

Important controls for the current game are as follows:

\begin{itemize}
    \item WASD Keys for player controlled movement in rm\_forest.
    \item Escape Key to return to rm\_forest from a combat encounter.
    \item Enter Key to interact with the NPC and leave the interaction.
\end{itemize}

Sincerely,

\tab Jacob Davis \\
\tab Caleb Jhones \\
\tab Robbie Merillat \\
\tab Jonathan Sumner Evans \\
\tab David Grisham \\

\end{document}

