\documentclass[12pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage[pdftex]{hyperref}
\usepackage[english]{babel}

\setlength\parindent{0pt}
\setlength\parskip{1em}

\newcommand\tab[1][.5in]{\hspace*{#1}}

\begin{document}

% For the team delivery, you need to submit a business letter to the publisher (i.e. me) describing
% the team along with three game ideas (paragraph for each).   This should be in a .doc, .docx or
% .pdf format.  Note, if you do not know how to construct a business letter, do a little research.

\hfill Epsilon Games

\hfill Jan 20, 2017

Mark Baldwin,

We are Epsilon Games, a newly formed game development company. We were founded with the purpose of
developing the most engaging, immersive, and enjoyable games on the market. To let you get a feel
for what our company is all about, we would like to present you with three of our best game
concepts. We hope to make one of these games a reality very soon.

In the coming weeks we plan on selecting a game to work on, and developing a project schedule. We
believe any of these games would be feasible to create within our timeframe, and we are excited to
begin working on one of them.

Sincerely,

\tab Jacob Davis \\
\tab Caleb Jhones \\
\tab Robbie Merillat \\
\tab Jonathan Sumner Evans \\
\tab David Grisham \\

\newpage
\section*{Key Deliverables}

\subsection*{Aeon Chronicles}
{\it Aeon Chronicles} is a Role playing Game with a unique item and combat system consisting of a card based system that is somewhat akin to a strategy game in that regard. The combat will be turn based and designed similarly to early final fantasy style of combat, however the attack/defense structure will be a card based combat system. These cards will be obtained from shops, battles, and found throughout the world. Due to the card based combat structure, there will be unique characters with customizable decks and a multitude of cards to make use of. Characters all have unique attacks and combat style however, the general format will be the same. Additionally they will have levels and as each player progresses through the game wither by level or by obtaining certain items, they will be able to use more and more cards in combat per turn. Player movement will be controlled via keyboard, and card selection in combat will be accessible via mouse clicks. Story is planned to be in depth and engaging and a significant part of the game.

\subsection*{Wizard Dragon}
{\it Wizard Dragon} is a rogue-like JRPG with unique character upgrade and battle systems. The game is played as a never ending boss rush fought by two player controlled characters, a mysterious wizard and a dragon knight. In each level of the game, hordes of enemies will assail the player followed by a boss for the level. In between each level, a shop will be accessible where potions and other helpful items can be purchased. The player will also be fully healed. When the player inevitably dies, a high score is recorded and ability points and starting gold are rewarded based on how far the player made it last run. These ability points can be used to upgrade each of the player controlled character's combat abilities and the gold can be spent in the shop before starting the next run.

\subsection*{Assassins Feed Four}

{\it Assassins Feed Four} is a side-scrolling beat 'em up game. In {\it AFF},
players choose among the ninja, sniper, and other assassins who need to feed
their families and do so by brawling their way through various worlds to collect
both food and money. Each world's theme is based on a unique economic system,
including capitalism, dictatorship, and communism. Fight your way through each
world while upgrading your character's skillset, all to feed your family of
four!



\end{document}
